AIR4children: Artificial Intelligence and Robotics for Children

### 2021-02-09 article/tex/submission.tex
adds ElvaCorona contribution

\section{Open AIR4Children}
[Section to describe the proposed project of air4children and the integration 
of opensource tools.]
The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

>>>>

\section{Open AIR4Children}
The general population, parents and children consider that Robotics is for people with a high IQ, engineers, complicated to learn, and too expensive, in one word, UNREACHABLE. We are working on changing this perception.   
AIR4CHILDREN proposes to bring Artificial Intelligence and Robotics (AIR) from laboratories to playgrounds, showing that robotics is intuitive, fun and accessible.  
AIR4CHILDREN is focused on achieving that AIR be perceived as a “game” or like a recreational activity, similar to swim, ride a bike, do chemical experiments, play chess, that the child says things like: “I want to play AIR (Robotics)”, “dear Santa Claus my wish is that you bring me a Robotic set”, “friend let's play to build a robot”.   
AIR4CHILDREN seeks to implement open hardware and software, which represents for parents an economically and accessible activity for their children.  
Formally, the AIR4CHILDREN project, in a first phase invites children, adolescents and young people to "play AIR" through calls to summer courses.   
The groups are formed according to their ages. In these courses we use different game-based learning techniques [refs], they are taught Artificial Intelligence and Robotics (construction and programming).   
During these activities they are observed in order to: i) discover individual and team skills, ii) develop their talents, and iii) monitor their growth.  
The programs and equipment used will be open, currently work with [refs], in section 3.1. looks more in detail.  
In the second phase, the children who took the course  are invited to be part of an AIR team, which will have permanent meetings, and will work on specific projects to participate on IAR competition events. In this case the groups are formed according to their capabilities.
On a third phase at least once a year we celebrate a public exposition, where the children talk with other children and their parents, showing their robots, sharing their experiences, and interacting between the public and the team so that the general population has a new perception of AIR.
The pilot project is being implemented in Xicohtzinco, a town from Tlaxcala, Mexico, with a population of, [refs].
